---
chapter: "simple models"
author: "Daniel Kaplan"
date: 2018-11-30 
version: 0.1
topics: [coverage interval, graphics]
id: bee-sell-blanket 
---

```{r bee-sell-blanket-default, include = FALSE}
SDSdata::sds_setup()
```

TITLE GOES HERE: The three graphs below show the distribution of weights broken down by sex. The violin layer is the same in each graph. Each graph has a coverage interval at one of these levels: 25% 50%, 80%, 95%. Which graph has which coverage interval? Which of the listed coverage intervals is not shown in any graph?



```{r bee-sell-blanket-1, echo = FALSE, fig.show = "hold", out.width = "33%"}
Dat <- NHANES %>%
  dplyr::select(Weight, Smoke100, Gender) %>%
  na.omit() 
Intervals <- df_stats(Weight ~ Gender, data = Dat, 
                      fifty = coverage(0.50), eighty = coverage(0.80), ninetyfive = coverage(0.95))
P <- gf_violin(Weight ~ Gender, data = Dat, alpha = 0.2, fill = ~ Gender, color = NA) %>%
  gf_theme(legend.position="none",axis.text = element_text(size = 20), 
           plot.title = element_text(size = 30)) %>%
  gf_labs(y = "Weight (lbs)", x = "")
P %>%  
  gf_errorbar(eighty_lower + eighty_upper ~ Gender, 
              alpha = 1, size = 2, color = ~ Gender, data = Intervals, width = 0.2) %>%
  gf_labs(title = "(a)")

P %>%  
  gf_errorbar(fifty_lower + fifty_upper ~ Gender, 
              alpha = 1, size = 2, color = ~ Gender, data = Intervals, width = 0.2) %>%
  gf_labs(title = "(b)")
P %>%  
  gf_errorbar(ninetyfive_lower + ninetyfive_upper ~ Gender, 
              alpha = 1, size = 2, color = ~ Gender, data = Intervals, width = 0.2) %>%
  gf_labs(title = "(c)")
```

-A- Graph (a) is 80%; Graph (b) is 50%; Graph (c) is 95%. There is no 25% interval shown. If there were, it would fit well within the 50% interval.
